\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-17 paper.tex
Revise up to sec. 4.3

\subsection{PS GRIN Single Layer }
\label{sec:ps-grin-single}
\notaL{Quité la figura pues no añade nada}
\notaL{Quité la descripción, pues está arriba}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \text{mA}$
    during a time $t_1=600\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\text{cm}$ and
    $x_C=1.7\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
que hagas tres figuras distintas, una para cada panel, y las alineamos
con latex}}
  \label{fig:DR3}
\end{figure}
 In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
 structures, $G_1$, prepared as described in
 \ref{sec:fabrication-ps-grin} applying a current $I_1=5\text{mA}$ for
 $t_1=600\text{s}$.\notaL{Quizás podamos quitar la repetición de I y
   t} We employed the same geometry as that described in
 Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
The position of electrode corresponds to the upper left side of the
photograph. The variation of the optical properties across the
sample is evident. We chose three positions $x_A=0.3\text{cm}$,
$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿Son correctos estos
  valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
which we measured the reflectance spectra, also shown in the figure.
We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity and the depth of the layer
as adjustable parameters. \notal{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
Location $A$ is
closest to the electrode, while location $C$ is the furthest.
\notaL{Quité una frase sin sentido.}
We also show in Fig. \ref{fig:DR3} the wavelength dependence of
 the complex index of refraction corresponding to the fitted porosities.
\notaL{Quité otra frase que no entendí, pero que me generó una duda:
  la profundidad la ajustaste ópticamente o la mediste en SEM y luego
  hiciste el ajuste a la reflectancia?}

@@

In Fig. \ref{fig:DR4} we shows side-view SEM micrographs taken at
positions $A$, $B$, and $C$ of sample $G_1$ shown in
Fig. \ref{fig:DR3}. From these micrographs we can
obtain the thicknesses of the porous layer at different
positions. Thus, we obtained that for our sample $G_1$
$d_{1A}= 1320\text{nm}$, $ d_{1B} = 997\text{nm}$, and $d_{1c} = 605
\text{nm}$. Similarly, for a second sample $G_2$, attacked with a
larger current $I_2 =40 \text{mA}$, for a time $t_2=$?\notaL{El ancho no
  tiene sentido si no especificas el tiempo} we obtained the
porosities \notaL{las posiciones ¿fueron las mismas?}, $p_{2A}= 0.76$, $p_{2B}=
0.73$, and $p_{2C}= 0.68$, and the corresponding depths $d_{2A}=1950\text{nm}$,
$d_{2B}=1690\text{nm}$, and $d_{2C}= 1430\text{nm}$. \notaL{Quité otra
  frase vacía}\notaL{Me es importante entenderte: La profundidad la
  obtuviste de SEM. ¿También la obtuviste de R, o primero la obtuviste
  de SEM y luego la sustituiste en la fórmula de R? Recuerdo que nos
  presentaste alguna vez que la profundidad obtenida de la óptica
  correspondía a la medida por SEM. ¿Fue así? Si sí, por qué no lo
  escribes aquí?}
   \includegraphics[width=\textwidth]{Images/grinJDR}
  \caption{(a)Current density calulated on different positions
    $A$, $B$, and $C$ along the samples $G_1$ and $G_2$ (as shown in
    Fig. \ref{fig:DR3}), for attack currents $I_1=5\text{mA}$ and
    $I_2=40\text{mA}$ (left panel), obtained by properly scaling the
    results of Fig. \ref{fig:DR1}. \notaL{Pon paréntesis de ambos
      lados (a) y (b). El eje horizontal es $x$, no $a$. El eje
      vertical es $j_\perp$.}
    (b)Attack speed $v=d/t$ obtained at different positions $A$, $B$,
    and $C$ over samples $G_1$ and $G_2$, where $d$ is the thickness
    as measured from SEM micrographs, as in Fig. \ref{fig:DR4},
    and $t$ is the attack time.}
  \label{fig:JDR}
In Fig. \ref{fig:JDR} a) It is the relation of the current density $ J
(mA / cm ^ 2) $ normalized with the electric current $ I (mA) $, we
have $ J / I \ sim 1.2 \ \ a \ \ 0.5 (1 / cm ^ 2) $, when we apply it
to two samples $ G1 (I = 5 \ \ mA) $ and $ G2 (I = 40 \ \ mA) $
depending on the axis $ a $ $ (0.1 ... 2.0 \ \ cm) $, measured at
points $ A (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
$.
The Fig. \ref{fig:JDR} b) we can calculate the attack speed $ v = d
(J_i) / t (nm / s) $, where the depths (thickness $ d (J_i) $, $ i = $
$ A (0.3 \ \ cm) $, $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)) $ taken
in SEM micrographs $ d (J_i) (nm) $ and attack times $ G1 (t = 600 \ \
s) $ and $ G2 (t = 200 \ \ s) $, depending on the axis $ a $ $ (0.1
... 2.0 \ \ cm) $.
  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{The relationship of samples $ G1 (I = 5 mA) $ and $
      G2 (I = 40 mA) $ were obtained to find: a) Attack speed with
      current density for each point and b) Porosity as a function of
      density current. With this we have the calibration curves for
      the manufacture of any GRIN porous silicon structure   }
  \label{fig:Indr1}
Fig. \ref{fig:Indr1} a) explicitly explain the relationships that
emerge when designing samples $ G1 (I = 5 mA) $ and $ G2 (I = 40 mA)
$. For the first case $ G1 $ the depths ($ 1320 \ \ nm $ to $ 605 \ \
nm $) and the current densities ($ 6 \ \ mA / cm ^ 2 $ to $ 2.5 \ \ mA
/ cm ^ 2 $), finding the attack speed $ 2.2 \ \ nm / s $ up to $ 1.1 \
\ nm / s $ relation with depth and the time ($ 600 \ \ s $) of
exposure of the sample, with the current density . We also find the
depth ($ 1950 \ \ nm $ at $ 1430 \ \ nm $) and the current density ($
50 \ \ mA / cm ^ 2 $ at $ 20 \ \ mA / cm ^ 2 $) as a function of the
measurement points of the sample $ G2 (I = 40 mA) $. We were able to
obtain the attack speed from $ 9.8 \ \ nm / s $ up to $ 7.1 \ \ m / s
$ by relating to depth and time ($ 200 \ \ s $), with current
density. Once the thickness of the monolayer and the attack time
applied to them are known, calculate the attack speed according to the
formula $ v = d / t $, for each of the current densities at the points
$ A ( 0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.7 \ \ cm)
$. Then we fit a function to the attack speed points with the
different current densities allowed by the anodizing condition. For a
desired thickness $ d (J_i) $, calculate the attack time $ t $ (so, $
t = v / d (J_i) $) and we can design any structure knowing the current
density and the attack time. Fig. \ref{fig:Indr1} b) we find a
relation of the porosity for each position with its determined current
density. Therefore, if it is desired to manufacture a PS monolayer of
a certain porosity with a certain end, it is enough to resort to the
graphs of Fig. \ref{fig:Indr1} to determine the corresponding current
density, attack speed and consequently the time, obtaining for that
monolayer. The importance of the calibration curves is that it allows
us to have a relationship of the porosities that can be reached (and
by having control over the possible refractive indices) as a function
of the current density and to be controlled to control the thickness
of the layers that are manufactured, by controlling the attack time
for each of the chosen currents.

>>>>

\subsection{PS GRIN Single Layer }
\label{sec:ps-grin-single}
\notaL{Quité la figura pues no añade nada}
\notaL{Quité la descripción, pues está arriba}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \text{mA}$
    during a time $t_1=600\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\text{cm}$ and
    $x_C=1.7\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
que hagas tres figuras distintas, una para cada panel, y las alineamos
con latex}}
  \label{fig:DR3}
\end{figure}
 In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
 structures, $G_1$, prepared as described in
 \ref{sec:fabrication-ps-grin} applying a current $I_1=5\text{mA}$ for
 $t_1=600\text{s}$.\notaL{Quizás podamos quitar la repetición de I y
   t} We employed the same geometry as that described in
 Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
The position of the electrode corresponds to the left side of the
photograph. The variation of the optical properties across the
sample is evident. We chose three positions $x_A=0.3\text{cm}$,
$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿Son correctos estos
  valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
which we measured the reflectance spectra, also shown in the figure.
We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity and the depth of the layer
as adjustable parameters. \notaL{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
Location $A$ is
closest to the electrode, while location $C$ is the furthest.
\notaL{Quité una frase sin sentido.}
We also show in Fig. \ref{fig:DR3} the wavelength dependence of
 the complex index of refraction corresponding to the fitted porosities.
\notaL{Quité otra frase que no entendí, pero que me generó una duda:
  la profundidad la ajustaste ópticamente o la mediste en SEM y luego
  hiciste el ajuste a la reflectancia?}

@@

In Fig. \ref{fig:DR4} we show side-view SEM micrographs of sample
$G_1$ taken at the
positions $A$, $B$, and $C$ shown in
Fig. \ref{fig:DR3}. From these micrographs we can
obtain the thicknesses of the porous layer at different
positions. Thus, we obtained that for our sample $G_1$
$d_{1A}= 1320\text{nm}$, $ d_{1B} = 997\text{nm}$, and $d_{1c} = 605
\text{nm}$. Similarly, for a second sample $G_2$, attacked with a
larger current $I_2 =40 \text{mA}$, for a time $t_2=$?\notaL{El ancho no
  tiene sentido si no especificas el tiempo} we obtained the
porosities \notaL{las posiciones ¿fueron las mismas que para $G_1$?}, $p_{2A}= 0.76$, $p_{2B}=
0.73$, and $p_{2C}= 0.68$, and the corresponding depths $d_{2A}=1950\text{nm}$,
$d_{2B}=1690\text{nm}$, and $d_{2C}= 1430\text{nm}$. \notaL{Quité otra
  frase vacía}\notaL{Me es importante entenderte: La profundidad la
  obtuviste de SEM. ¿También la obtuviste de R, o primero la obtuviste
  de SEM y luego la sustituiste en la fórmula de R? Recuerdo que nos
  presentaste alguna vez que la profundidad obtenida de la óptica
  correspondía a la medida por SEM. ¿Fue así? Si sí, por qué no lo
  escribes aquí?}

\begin{figure}
  \centering
   \includegraphics[width=\textwidth]{Images/grinJDR}
  \caption{(a)Current density calculated by scaling the results of
    Fig. \ref{fig:DR1} by the currents $I_1=5\text{mA}$ and
    $I_2=40\text{mA}$ used to prepare samples $G_1$ and $G_2$.
. \notaL{Pon paréntesis de ambos
      lados (a) y (b). El eje horizontal es $x$, no $a$. El eje
      vertical es $j_\perp$.}
    (b)Etching rate speed $v=d/t$ obtained at different positions $A$, $B$,
    and $C$ over samples $G_1$ and $G_2$, where $d$ is the thickness
    as measured from SEM micrographs, as in Fig. \ref{fig:DR4},
    and $t$ is the etching time.\notaL{Falta una gráfica similar de
      porosidad vs. x para las dos muestras}\notaL{Las escalas del
      lado derecho no tienen que ver con las del lado
      izquierdo. Deberías poner la misma escala de ambos lados, con el
    mismo quiebre.}\notaL{Sugiero en la gráfica de la corriente
    graficar las dos líneas completas, además de los 6 puntos
    correpondientes a A, B y C de las dos muestras}}
  \label{fig:JDR}
\end{figure}
In Fig. \ref{fig:JDR}(a) we show the actual current current density
$j_\perp$ obtained from Fig. \ref{fig:DR1} by scaling by the actual
current $I_1=5\text{mA}$ and $I_2=40\text{mA}$ employed to prepare
samples $G_1$ and $G_2$, respectively. We indicate the values
corresponding to positions $A$, $B$, and $C$ on the samples.
\notaL{la
  corriente que muestras no es normalizada}
In Fig. \ref{fig:JDR} (b) we show the etching rate $v = d/t$ on
selected positions of both samples obtained by dividing the thickness
$d$ measured as in Fig. \ref{fig:DR4} by the etching time.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
    show the data points and the results of power
    law fits, yielding $v=0.53j_\perp^{0.79}$ and
    $p=0.3j_\perp^0.24$, with corresponding correlation coefficients
      $r_v^2=0.993$ and $r_p^2=0.989$ (here $v$ is in nm/s, $p$ is
      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
      por $p$. Quita el letrero fitting data, la ecuación y el valor
      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
  \label{fig:Indr1}
\end{figure}
By relating among themselves the panels of Fig. \ref{fig:JDR} we
may obtain the etching rate $v$ and the porosity $p$ as
functions of the current density $j_\perp$. The results are shown in
Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
  tiempo de ataque de la muestra dos: relating to depth and time ($
  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
We fitted the data points with simple power laws and found
$v=0.53j_\perp^{0.79}$ and $p=0.3j_\perp^{0.24}$, where $v$ is
expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.993$
and $r_p^2=0.989$. \notaL{Digresión teórica. El producto $pv$ es
  proporcional a la cantidad de materia removida por segundo. En mi
  opinión, esto debería ser proporcional a la corriente $pv\propto
  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
  esto se tiene que rehacer usando la expresión teórica correcta y las
  posiciones correctas}

Fig. \ref{fig:Indr1} illustrates an advantage of using a cell
geometry for which the current density may be obtained
analytically. Namely, we can relate the etching rate and the
porosity to the current density by taking measurements at
different positions along just a few PS GRIN samples. Thus, it is much easier
and faster to obtain calibration curves which are useful in the
fabrication of PS photonic structures, GRIN or otherwise.
